Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-04 paper.qmd
Update Figure 8

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = b, 
                         y = log(MSE))) + 
  geom_point(size = 1) +
  geom_line() + 
  geom_vline(xintercept = 190, linetype="solid", 
             color = "black", linewidth=0.8, alpha = 0.5) +
  geom_vline(xintercept = 91, linetype=2, 
             color = "black", linewidth=0.8, alpha = 0.5) +
  geom_vline(xintercept = 364, linetype=2, 
             color = "black", linewidth=0.8, alpha = 0.5) +
  ylab("log(MSE)") +
  xlab("b") +
  ggtitle("(a)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 5),
        axis.text.y = element_text(size = 5),
        axis.title.x = element_text(size = 5),
        axis.title.y = element_text(size = 5, 
            angle=90),
        title = element_text(size = 72))
```

>>>>

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = b, 
                         y = log(MSE))) + 
  geom_point(size = 1) +
  geom_line() + 
  geom_vline(xintercept = 240, linetype="solid", 
             color = "black", linewidth=0.8, alpha = 0.5) +
  geom_vline(xintercept = 96, linetype=2, 
             color = "black", linewidth=0.8, alpha = 0.5) +
  geom_vline(xintercept = 375, linetype=2, 
             color = "black", linewidth=0.8, alpha = 0.5) +
  ylab("log(MSE)") +
  xlab("b") +
  ggtitle("(a)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 5),
        axis.text.y = element_text(size = 5),
        axis.title.x = element_text(size = 5),
        axis.title.y = element_text(size = 5, 
            angle=90),
        title = element_text(size = 72))
```
